---
title: "4.5.17 The Long Exodus Gets Somewhere, Milestone 2"
author: "Craig Alder"
date: "4/5/2017"
output: html_document
---
I have worked really hard developing this code and learned that the internet R discussions extend deep into the internet -- and it finally works! The printout at the end of this document is a sample of what it pulls. I can apply this same form to the rest of the blogs. You can also see the other variables I have collected and the extensive preparation of html at [https://docs.google.com/spreadsheets/d/1zxiNYbXcBGu8K20ZpYdut8ihJFLYanl3i-tdSv0TagQ/edit#gid=0] (https://docs.google.com/spreadsheets/d/1zxiNYbXcBGu8K20ZpYdut8ihJFLYanl3i-tdSv0TagQ/edit#gid=0). My repository should have documentation of the extensive work it took to get this seemingly simple code. Next week I will run the topic modelling with the librarian I've been working with, so I can then plot the data.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rvest)    
url <-  "http://www.ashleyannphotography.com/blog/2017/04/02/canopy-anna-turner/"

getPostContent <- function(url){
    Sys.sleep(2)
    read_html(url) %>% 
        html_nodes(".article-content")%>%           
        html_text() %>% 
        gsub(x = ., pattern = '[\a\t\n]', replacement = '')
       # Sys.sleep(2)
}

getDate <- function(url) {
    Sys.sleep(.3)
    read_html(url) %>% 
        html_node(".updated") %>%
        html_text()
   #     Sys.sleep(1:3)
}

getTitle <- function(url) {
    Sys.sleep(.8)
    read_html(url) %>% 
        html_node(".article-title") %>%
        html_text()
       # Sys.sleep(1:3)
}

getNextUrl <- function(url) {
    Sys.sleep(.2)
    read_html(url) %>% 
        html_node(".prev-post-link-wrap a") %>%
        html_attr("href")
   #     Sys.sleep(1:3)
}

scrapeBackMap <- function(url, n) {
    Sys.sleep(1.6)
    purrr::map_df(1:n, ~{
        oUrl <- url
        date <- getDate(url)
        post <- getPostContent(url)
        title <- getTitle(url)
        url <<- getNextUrl(url)
        
        data.frame(curpage = oUrl, 
                        nexturl = url,
                        posttext = post,
                        pubdate = date,
                        ptitle = title
                        )
    })
}

res <- scrapeBackMap(url, 3)
class(res)
str(res)
```
The link to my Github account is [https://github.com/craigalder](https://github.com/craigalder). The link to my repository for this project is [https://github.com/craigalder/NSRG741_AlderProject](https://github.com/craigalder/NSRG741_AlderProject).