---
title: "4.5.17 The Long Exodus Gets Somewhere, Milestone 2"
author: "Craig Alder"
date: "4/5/2017"
output: html_document
---
I have worked really hard developing this code and learned that the internet R discussions extend deep into the internet -- and it finally works! The printout at the end of this document is a sample of what it pulls. I can apply this same form to the rest of the blogs. You can also see the other variables I have collected and the extensive preparation of html at [https://docs.google.com/spreadsheets/d/1zxiNYbXcBGu8K20ZpYdut8ihJFLYanl3i-tdSv0TagQ/edit#gid=0] (https://docs.google.com/spreadsheets/d/1zxiNYbXcBGu8K20ZpYdut8ihJFLYanl3i-tdSv0TagQ/edit#gid=0). My repository should have documentation of the extensive work it took to get this seemingly simple code. Next week I will run the topic modelling with the librarian I've been working with, so I can then plot the data.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rvest)  
library(purrr)
url <- "https://dooce.com/2017/04/06/dooce-fourteen-hundred-and-ninety-point-two/"
#Select first page.

getPostContent <- function(url){
    Sys.sleep(.2)
    #Introduces pauses to convince server not robot.
    read_html(url) %>% 
        html_nodes(".post_content") %>% 
       #html_nodes(".individual-post>:not([div.postbottomright])") %>%
        html_text()
        #gsub(x = ., pattern = '[\n]', replacement = ' ')
    }
#Pulls node for post content.

#Pulls node for date.
getDate <- function(url) {
    Sys.sleep(.8)
    read_html(url) %>% 
        html_node(".post-date") %>%
        html_text()
}

getTitle <- function(url){
    Sys.sleep(1.1)
    read_html(url) %>% 
        html_node("title") %>%
        html_text() %>%
       gsub(pattern = 'dooce®', replacement = '',x= .)
}
#Pulls node for title.

getNextUrl <- function(url) {
    Sys.sleep(.2)
    read_html(url) %>% 
        html_nodes(".prev-post-link a") %>%
        html_attr("href")
    }
#Pulls node for url to previous post.

scrapeBackMap <- function(url, n){
    Sys.sleep(1.9)
    purrr::map_df(1:n, ~{
        if(!is.na(url)){
        oUrl <- url
        date <- getDate(url)
        post <- getPostContent(url)
        title <- getTitle(url)
        url <<- getNextUrl(url)
           
        data.frame(curpage = oUrl, 
                        nexturl = url,
                        posttext = post,
                        pubdate = date,
                        ptitle = title
#prepares functions for dataframe
                        )}
    })
}
   df_dooce1 <- scrapeBackMap(url, 2500)
   class(df_dooce1)
   str(df_dooce1)
#creates dataframe
   
save(df_dooce1,file="DooceScrape_1.Rda")
```

```{r}
library(rvest)    
url <- "df_dooce1$nexturl[[2500]]"
#Select first page.

getPostContent <- function(url){
    Sys.sleep(.2)
    #Introduces pauses to convince server not robot.
    read_html(url) %>% 
        html_nodes(".post_content") %>% 
       #html_nodes(".individual-post>:not([div.postbottomright])") %>%
        html_text()
        #gsub(x = ., pattern = '[\n]', replacement = ' ')
    }
#Pulls node for post content.


#Pulls node for date.
getDate <- function(url) {
    Sys.sleep(.8)
    read_html(url) %>% 
        html_node(".post-date") %>%
        html_text()
}

getTitle <- function(url){
    Sys.sleep(1.1)
    read_html(url) %>% 
        html_node("title") %>%
        html_text() %>%
       gsub(pattern = 'dooce®', replacement = '',x= .)
}
#Pulls node for title.

getNextUrl <- function(url) {
    Sys.sleep(.2)
    read_html(url) %>% 
        html_node(".prev-post-link a") %>%
        html_attr("href")
    }
#Pulls node for url to previous post.

scrapeBackMap <- function(url, n){
    Sys.sleep(1.9)
    purrr::map_df(1:n, ~{
    if(!is.na(url)){
        oUrl <- url
        date <- getDate(url)
        post <- getPostContent(url)
        title <- getTitle(url)
        url <<- getNextUrl(url)
           
        data.frame(curpage = oUrl, 
                        nexturl = url,
                        posttext = post,
                        pubdate = date,
                        ptitle = title
#prepares functions for dataframe
                        )}
    })
}
   df_dooce2 <- scrapeBackMap(url, 100)
   class(df_dooce2)
   str(df_dooce2)
#creates dataframe
   
save(df_dooce2,file="DooceScrape_2.Rda")
```

```{r}
library(rvest)    
url <- "https://dooce.com/2011/03/01/nine-years/"
#Select first page.

getPostContent <- function(url){
    Sys.sleep(.2)
    #Introduces pauses to convince server not robot.
    read_html(url) %>% 
        html_nodes(".post_content") %>% 
       #html_nodes(".individual-post>:not([div.postbottomright])") %>%
        html_text()
        #gsub(x = ., pattern = '[\n]', replacement = ' ')
    }
#Pulls node for post content.


#Pulls node for date.
getDate <- function(url) {
    Sys.sleep(.8)
    read_html(url) %>% 
        html_node(".post-date") %>%
        html_text()
}

getTitle <- function(url){
    Sys.sleep(1.1)
    read_html(url) %>% 
        html_node("title") %>%
        html_text() %>%
       gsub(pattern = 'dooce®', replacement = '',x= .)
}
#Pulls node for title.

getNextUrl <- function(url) {
    Sys.sleep(.2)
    read_html(url) %>% 
        html_node(".prev-post-link a") %>%
        html_attr("href")
    }
#Pulls node for url to previous post.

scrapeBackMap <- function(url, n){
    Sys.sleep(1.9)
    purrr::map_df(1:n, ~{
    if(!is.na(url)){
        oUrl <- url
        date <- getDate(url)
        post <- getPostContent(url)
        title <- getTitle(url)
        url <<- getNextUrl(url)
           
        data.frame(curpage = oUrl, 
                        nexturl = url,
                        posttext = post,
                        pubdate = date,
                        ptitle = title
#prepares functions for dataframe
                        )}
    })
}
   df_dooce3 <- scrapeBackMap(url, 2000)
   class(df_dooce3)
   str(df_dooce3)
#creates dataframe
   
save(df_dooce3,file="DooceScrape_3.Rda")
```
```{r}
library(rvest)    
url <- df_dooce5$nexturl[2000]
#Select first page.

getPostContent <- function(url){
    Sys.sleep(.2)
    #Introduces pauses to convince server not robot.
    read_html(url) %>% 
        html_nodes(".post_content") %>% 
       #html_nodes(".individual-post>:not([div.postbottomright])") %>%
        html_text()
        #gsub(x = ., pattern = '[\n]', replacement = ' ')
    }
#Pulls node for post content.


#Pulls node for date.
getDate <- function(url) {
    Sys.sleep(.8)
    read_html(url) %>% 
        html_node(".post-date") %>%
        html_text()
}

getTitle <- function(url){
    Sys.sleep(1.1)
    read_html(url) %>% 
        html_node("title") %>%
        html_text() %>%
       gsub(pattern = 'dooce®', replacement = '',x= .)
}
#Pulls node for title.

getNextUrl <- function(url) {
    Sys.sleep(.2)
    read_html(url) %>% 
        html_node(".prev-post-link a") %>%
        html_attr("href")
    }
#Pulls node for url to previous post.

scrapeBackMap <- function(url, n){
    Sys.sleep(1.9)
    purrr::map_df(1:n, ~{
    if(!is.na(url)){
        oUrl <- url
        date <- getDate(url)
        post <- getPostContent(url)
        title <- getTitle(url)
        url <<- getNextUrl(url)
           
        data.frame(curpage = oUrl, 
                        nexturl = url,
                        posttext = post,
                        pubdate = date,
                        ptitle = title
#prepares functions for dataframe
                        )}
    })
}
   df_dooce4 <- scrapeBackMap(url, 500)
   class(df_dooce4)
   str(df_dooce4)
#creates dataframe
   
save(df_dooce4,file="DooceScrape_4.Rda")
```


```{r}
library(rvest)    
url <- df_dooce4$nexturl[500]
#Select first page.

getPostContent <- function(url){
    Sys.sleep(.2)
    #Introduces pauses to convince server not robot.
    read_html(url) %>% 
        html_nodes(".post_content") %>% 
       #html_nodes(".individual-post>:not([div.postbottomright])") %>%
        html_text()
        #gsub(x = ., pattern = '[\n]', replacement = ' ')
    }
#Pulls node for post content.


#Pulls node for date.
getDate <- function(url) {
    Sys.sleep(.8)
    read_html(url) %>% 
        html_node(".post-date") %>%
        html_text()
}

getTitle <- function(url){
    Sys.sleep(1.1)
    read_html(url) %>% 
        html_node("title") %>%
        html_text() %>%
       gsub(pattern = 'dooce®', replacement = '',x= .)
}
#Pulls node for title.

getNextUrl <- function(url) {
    Sys.sleep(.2)
    read_html(url) %>% 
        html_node(".prev-post-link a") %>%
        html_attr("href")
    }
#Pulls node for url to previous post.

scrapeBackMap <- function(url, n){
    Sys.sleep(1.9)
    purrr::map_df(1:n, ~{
    if(!is.na(url)){
        oUrl <- url
        date <- getDate(url)
        post <- getPostContent(url)
        title <- getTitle(url)
        url <<- getNextUrl(url)
           
        data.frame(curpage = oUrl, 
                        nexturl = url,
                        posttext = post,
                        pubdate = date,
                        ptitle = title
#prepares functions for dataframe
                        )}
    })
}
   df_dooce5 <- scrapeBackMap(url, 500)
   class(df_dooce5)
   str(df_dooce5)
#creates dataframe
   
save(df_dooce5,file="DooceScrape_5.Rda")
```

```{r}
library(rvest)    
url <- df_dooce5$nexturl[500]
#Select first page.

getPostContent <- function(url){
    Sys.sleep(.2)
    #Introduces pauses to convince server not robot.
    read_html(url) %>% 
        html_nodes(".post_content") %>% 
       #html_nodes(".individual-post>:not([div.postbottomright])") %>%
        html_text()
        #gsub(x = ., pattern = '[\n]', replacement = ' ')
    }
#Pulls node for post content.


#Pulls node for date.
getDate <- function(url) {
    Sys.sleep(.8)
    read_html(url) %>% 
        html_node(".post-date") %>%
        html_text()
}

getTitle <- function(url){
    Sys.sleep(1.1)
    read_html(url) %>% 
        html_node("title") %>%
        html_text() %>%
       gsub(pattern = 'dooce®', replacement = '',x= .)
}
#Pulls node for title.

getNextUrl <- function(url) {
    Sys.sleep(.2)
    read_html(url) %>% 
        html_node(".prev-post-link a") %>%
        html_attr("href")
    }
#Pulls node for url to previous post.

scrapeBackMap <- function(url, n){
    Sys.sleep(1.9)
    purrr::map_df(1:n, ~{
    if(!is.na(url)){
        oUrl <- url
        date <- getDate(url)
        post <- getPostContent(url)
        title <- getTitle(url)
        url <<- getNextUrl(url)
           
        data.frame(curpage = oUrl, 
                        nexturl = url,
                        posttext = post,
                        pubdate = date,
                        ptitle = title
#prepares functions for dataframe
                        )}
    })
}
   df_dooce6 <- scrapeBackMap(url, 1000)
   class(df_dooce6)
   str(df_dooce6)
#creates dataframe
   
save(df_dooce6,file="DooceScrape_6.Rda")
```

```{r}
library(rvest)   
####This is causing problems because one of the pages, post is titled here we are as in olden days, was removed
url <- "https://dooce.com/2005/01/04/hammer-time/"
#Select first page.

getPostContent <- function(url){
    Sys.sleep(.2)
    #Introduces pauses to convince server not robot.
    read_html(url) %>% 
        html_nodes(".post_content") %>% 
       #html_nodes(".individual-post>:not([div.postbottomright])") %>%
        html_text()
        #gsub(x = ., pattern = '[\n]', replacement = ' ')
    }
#Pulls node for post content.


#Pulls node for date.
getDate <- function(url) {
    Sys.sleep(.8)
    read_html(url) %>% 
        html_node(".post-date") %>%
        html_text()
}

getTitle <- function(url){
    Sys.sleep(1.1)
    read_html(url) %>% 
        html_node("title") %>%
        html_text() %>%
       gsub(pattern = 'dooce®', replacement = '',x= .)
}
#Pulls node for title.

getNextUrl <- function(url) {
    Sys.sleep(.2)
    read_html(url) %>% 
        html_node(".prev-post-link a") %>%
        html_attr("href")
    }
#Pulls node for url to previous post.

scrapeBackMap <- function(url, n){
    Sys.sleep(1.9)
    purrr::map_df(1:n, ~{
    if(!is.na(url)){
        oUrl <- url
        date <- getDate(url)
        post <- getPostContent(url)
        title <- getTitle(url)
        url <<- getNextUrl(url)
           
        data.frame(curpage = oUrl, 
                        nexturl = url,
                        posttext = post,
                        pubdate = date,
                        ptitle = title
#prepares functions for dataframe
                        )}
    })
}
   df_dooce7 <- scrapeBackMap(url, 3)
   class(df_dooce7)
   str(df_dooce7)
#creates dataframe
   
save(df_dooce7,file="DooceScrape_7.Rda")
```

```{r}
library(rvest)    
url <- df_dooce7$nexturl[1000]
#Select first page.

getPostContent <- function(url){
    Sys.sleep(.2)
    #Introduces pauses to convince server not robot.
    read_html(url) %>% 
        html_nodes(".post_content") %>% 
       #html_nodes(".individual-post>:not([div.postbottomright])") %>%
        html_text()
        #gsub(x = ., pattern = '[\n]', replacement = ' ')
    }
#Pulls node for post content.


#Pulls node for date.
getDate <- function(url) {
    Sys.sleep(.8)
    read_html(url) %>% 
        html_node(".post-date") %>%
        html_text()
}

getTitle <- function(url){
    Sys.sleep(1.1)
    read_html(url) %>% 
        html_node("title") %>%
        html_text() %>%
       gsub(pattern = 'dooce®', replacement = '',x= .)
}
#Pulls node for title.

getNextUrl <- function(url) {
    Sys.sleep(.2)
    read_html(url) %>% 
        html_node(".prev-post-link a") %>%
        html_attr("href")
    }
#Pulls node for url to previous post.

scrapeBackMap <- function(url, n){
    Sys.sleep(1.9)
    purrr::map_df(1:n, ~{
    if(!is.na(url)){
        oUrl <- url
        date <- getDate(url)
        post <- getPostContent(url)
        title <- getTitle(url)
        url <<- getNextUrl(url)
           
        data.frame(curpage = oUrl, 
                        nexturl = url,
                        posttext = post,
                        pubdate = date,
                        ptitle = title
#prepares functions for dataframe
                        )}
    })
}
   df_dooce8 <- scrapeBackMap(url, 1000)
   class(df_dooce8)
   str(df_dooce8)
#creates dataframe
   
save(df_dooce8,file="DooceScrape_8.Rda")
```